Modeling vertical-axis cross-flow turbine wakes

### 2015-07-20 paper.tex
Add to case description

% Use the \preprint command to place your local institutional report number 
% on the title page in preprint mode.
% Multiple \preprint commands are allowed.
%\preprint{}

@@

The RANS models employ a sliding mesh, where the turbine zone rotates at a mean
tip speed ratio $\lambda=1.9$ with an unsteadiness as the blade passage
frequency specified to mimic the experimental data. The 2-D mesh is shown in
Figure~\ref{fig:mesh}.

To capture the boundary layer,

@@

>>>>

% Use the \preprint command to place your local institutional report number 
% on the title page in preprint mode.
% Multiple \preprint commands are allowed.
\preprint{}

@@

The computational domain is a rectangular volume

\todo[inline]{Add domain extent in terms of turbine diameter.}

 with a cylindrical sliding mesh
interface, where the turbine zone rotates at a mean tip speed ratio
$\lambda=1.9$ with an unsteadiness as the blade passage frequency specified to
mimic the experimental data. The 2-D mesh is shown in Figure~\ref{fig:mesh}.

The mesh topology is kept constant, while its refinement is controlled by a
single parameter---the number of cells in the streamwise direction, $N_x$.

To capture the boundary layer, 20 layers are

In the 3-D mesh, layers are not added to the struts and shaft to save
computational expense.

@@

\subsection{Initial and boundary conditions}

Initial and boundary conditions were set to match those of the tow tank as well
as possible.
